---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

# homework

The `homework` package let's R teachers automatically check homeworks that they are giving to their students. A recommended workflow is to have a master directory for all homework files, and then a sub-directory for each homework assignment. The base directory will have a `check_hw_master.R` master file to include the code to check homework everyweek. A subfolder of homework (say, HW01, HW02, etc.), will have a folder with the submissions of the students (called "submissions"), an R file with the correct solutions (it should be called solutions.R or hw01_solutions.R). An answer for each homework question should be a function (for example "write a function that calculates the sum a vector"). The solution file should include an object called `tests_to_run` at the end of it. This file is a nested list, each element of the list is a name of a function that the hw has asked for, and in it is either a list of possible inputs to check against the function, OR, a list of lists, each sublist will check some other input. After running the `check_hw` on the subdirectory "HW01", the function will create a "mistakes" folder with a list of which mistakes were found for each question/student, and a "grades" folder, with a csv including the grades of students (based on the filenames the students submit). The standard of the filenames of hw assignment is assingment_number_student_id.R (e.g.: 01_123456.R).

An example of a folder structure before running check_hw:

```
hw
-check_hw_master.R
-hw01
--submissions
---01_123456.R
---01_456987.R
---01_879456.R
--hw01_solutions.R (includes the corrects functions and the inputs to check)
--hw.txt/hw.pdf/hw.docx/etc. (ignored)
-hw02
--...
-hw03
--...
```

Folder structure AFTER running check_hw:

```
hw
-check_hw_master.R
-hw01
--submissions
---01_123456.R
---01_456987.R
---01_879456.R
--hw01_solutions.R (includes the corrects functions and the inputs to check)
--mistakes
---mistakes_in_foo.R
---mistakes_in_bar.R
--grades
---grades.csv
---grades_for_students.csv
--hw.txt/hw.pdf/hw.docx/etc. (ignored)
-hw02
--...
-hw03
--...
```


## Installation

You can install homework from github with:

```{r gh-installation, eval = FALSE}
# install.packages("devtools")
devtools::install_github("talgalili/homework")
```

## Example

The package comes with a simple example. The following code shows where the example is, and how to run a homework check on it.

Some of the homework file have intentional problems in them to deomnstrate how the function is able to deal with them:


```{r example}
library(homework)
demo_base_dir <- file.path(system.file(package = "homework"), "extdata")
demo_base_dir
check_hw("HW01", demo_base_dir)

```
